Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants with Transient Performance Specifications

### 2017-06-29 automatica/paper.tex
removed useless comment for Elizabeth
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
Proof for feedback model with continuous plant and discrete controller

>>>>

 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsubsection{Discrete dynamics using reals for systems with discrete time feedback inputs}\label{sec:real_discrete_feedback_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
The final case we analyse here is that of hybrid time systems, where the plant dynamics evolve in continuous time
while the feedback dynamics evolve in discrete time.

\begin{theorem}
The expression
 \begin{align}
 \vec{x}_{t} &= (\mat{A}_{t-kT_s}-\mat{B}_{t-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
 \end{align}
 with $\mat{A}_t, \mat{B}_t$ as per \eqref{eq:continuous_tube_dyn} and $\mat{A}_d, \mat{B}_d$ as per equation \eqref{eq:discretize} is a witness of the system
 \begin{align}
 \dot{\vec{x}}_{t} &= \mat{A}\vec{x}+\mat{B}\vec{u}_t\nonumber\\
 \vec{u}_t=\mat{K}\vec{x}_k  : kT_s \leq t < (k+1)T_s
 \end{align}
 \end{theorem}

\begin{proof}
Let $\mat{K}$ be a feedback controller such that $\vec{u}_k=-\mat{K}\vec{x}_k$ at time $t=kT_s$. Let the output of
the feedback system be a zero order holder such that $\vec{u}(t+kT_s)=\vec{u}(kT_s) : 0 \leq t < T_s$.
The closed loop dynamics of the system between times $kT_s$ and $kT_s+T_s$ are
\begin{equation}
\vec{x}_{k,t}=\mat{A}_t\vec{x}_k-\mat{B}_t\mat{K}\vec{x}_k = (\mat{A}_t-\mat{B}_t\mat{K})\vec{x}_k : 0 \leq t < T_s
\end{equation}
We further explore the dynamics across discrete time boundaries. Let $\mat{A}_d=\mat{A}_{T_s}$ and $\mat{B}_d=\mat{B}_{T_s}$
\begin{align}
\vec{x}_{k}&=\vec{x}_{k-1,T_s}= (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}\\
\vec{x}_{k,T_s} &= (\mat{A}_d-\mat{B}_d\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})\vec{x}_{k-1}
\end{align}
which accelerating results becomes
\begin{align}
\vec{x}_{k} &= (\mat{A}_d-\mat{B}_d\mat{K}) ^k\vec{x}_0\\
\vec{x}_{t} &= (\mat{A}_{t-kT_s}-\mat{B}_{t-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0
\end{align}
\end{proof}
